---
title: "EDAV Community Contribution Fall 2024"
author: Sstuti D Mehra (sdm2194)
format:
  html:
    embed-resources: true
execute: 
  echo: true
---

## The Chord Diagram

The chord diagram is useful to visualize flow from one entity to another to understand the volume and direction of flow from source to destination.

### Analyzing Website Traffic

The example below takes sample data from a hypothetical website on how users transition between pages of the website. This is important to visualize to understand engagement on the website and to understand the improvements to be implemented.

```{r}
library(igraph)

# Loading the website engagement data
website_navigation_data <- read.csv("website_navigation.csv")

# Converting the dataframe into a matrix
navigation_matrix <- as.matrix(as_adjacency_matrix(as_tbl_graph(website_navigation_data), attr = "counts"))

print(navigation_matrix)

```

```{r}
library(circlize)

pageColors <- c(Home="blue", AboutUs="orange", Services="green", Blog="purple", Contact="red", FAQ="cyan", Login="magenta", SignUp="yellow")

# Using the circlize package to create the chord diagram
chordDiagram(navigation_matrix, 
             grid.col = pageColors)

title(main = "User Journey on TechForward.com", cex.main = 1.5, font.main = 4)

```

```{r}
# Using the chorddiag package imported from GitHub to introduce interactivity to the chord diagram
library(chorddiag)

pageColors <- c("blue", "orange", "green", "purple", "red", "cyan", "magenta", "yellow")

chorddiag(navigation_matrix, groupColors = pageColors, showTicks = FALSE, margin = 90)

```

```{r}
htmlwidgets::saveWidget(chorddiag(navigation_matrix, groupColors = pageColors, showTicks = FALSE, margin = 90), "chord_diag.html")
```
